Formation of $\cenn$ Molecules in Oxygen-rich Interiors of Type II Supernovae

### 2013-01-23 doc/submit/ms.tex
Add submit/. The eps files may be useful in the future.

\begin{figure}
\plotone{figures/ncoeq.pdf}
\caption{
Comparison of the density of CO molecules calculated by the numerical
network (curve) with the expectation $\ncogeq = n_C n_O k_{CO} \tau_\gamma$
for an abundance
$n_{CO}$ in thermal equilibrium (dots) with photons.
Above T=4000K the CO abundance is seen to be in an accurate thermal
equilibrium, but at lower temperature $n_{CO}$ is increasingly smaller than
thermal equilibrium would require. Instead of thermal photons,
the destruction of CO becomes increasingly dominated by
Compton electrons for $T < 3500$ K.
One see in Fig. \ref{fig:nco} that $n_{CO}$max occurs near 3500K,
which occurs near $10^7$ s (see Table \ref{tab:quantities})}. 
\label{fig:nco}
\end{figure}

@@

\begin{figure}
\plotone{figures/co_flows.pdf}
\caption{
Flows into and out of CO illustrate the near steady state between creation
and destruction and the transition region near 3500K between the two modes
of destruction of CO.
The destruction flow $n_{CO} n_C k_{CO+C}$ is only $3.27 \times
10^{-16}$ atom$^{-1}$s$^{-1}$, too small to be visible in Fig. \ref{fig:flows}. 
} \label{fig:flows}
\end{figure}

@@

\begin{figure}
\plotone{figures/nco.pdf}
\caption{
Number densities of CO and of $\ctwo$\ as functions of temperature.
The maximum density of $\ctwo$\ is 0.1 cm$^{-3}$.
Both abundances grow much more slowly than in the calculation by
\citet{2009ApJ...703..642C}.} \label{fig:ncoc2}
\end{figure}

@@

\begin{figure}
\plotone{figures/Yi.pdf}
\caption{
The abundance (number per atom) of linear chains $\cenn$\ and of ringed isomer
$\ceightr$. We have scaled each $Y(C_n)$ by the factor stated in the box.}
\label{fig:yi}
\end{figure}

@@

\begin{figure}
\plotone{figures/cn.pdf}
\caption{
Shape of $Y(C_n)$ vs. n for $\cthree$\ to $\ceight$
at two different temperatures
near 2000K. These shapes can be understood by the relative magnitudes of
flows into and out of $\cenn$.
}
\label{fig:cn}
\end{figure}

@@

\begin{figure}
\plotone{figures/no_gamma.pdf}
\caption{
Abundances for network containing only C, O, CO, $\ctwo$, and $\cthree$
when photodissociation of molecules is omitted. Rapid rise of $Y(CO)$
to $10^{-2}$ near 5500 K and the ratio $Y(CO)/Y(\ctwo)$ near $10^4$ are
similar to Fig. 11 of \citet{2009ApJ...703..642C}.
}
\label{fig:no_gamma}
\end{figure}

@@

\bibliographystyle{apj}
\bibliography{clemson}

>>>>

\begin{figure}
\plotone{ncoeq}
\caption{
Comparison of the density of CO molecules calculated by the numerical
network (curve) with the expectation $\ncogeq = n_C n_O k_{CO} \tau_\gamma$
for an abundance
$n_{CO}$ in thermal equilibrium (dots) with photons.
Above T=4000K the CO abundance is seen to be in an accurate thermal
equilibrium, but at lower temperature $n_{CO}$ is increasingly smaller than
thermal equilibrium would require. Instead of thermal photons,
the destruction of CO becomes increasingly dominated by
Compton electrons for $T < 3500$ K.
One see in Fig. \ref{fig:nco} that $n_{CO}$max occurs near 3500K,
which occurs near $10^7$ s (see Table \ref{tab:quantities})}. 
\label{fig:nco}
\end{figure}

@@

\begin{figure}
\plotone{co_flows}
\caption{
Flows into and out of CO illustrate the near steady state between creation
and destruction and the transition region near 3500K between the two modes
of destruction of CO.
The destruction flow $n_{CO} n_C k_{CO+C}$ is only $3.27 \times
10^{-16}$ atom$^{-1}$s$^{-1}$, too small to be visible in Fig. \ref{fig:flows}. 
} \label{fig:flows}
\end{figure}

@@

\begin{figure}
\plotone{nco}
\caption{
Number densities of CO and of $\ctwo$\ as functions of temperature.
The maximum density of $\ctwo$\ is 0.1 cm$^{-3}$.
Both abundances grow much more slowly than in the calculation by
\citet{2009ApJ...703..642C}.} \label{fig:ncoc2}
\end{figure}

@@

\begin{figure}
\plotone{Yi}
\caption{
The abundance (number per atom) of linear chains $\cenn$\ and of ringed isomer
$\ceightr$. We have scaled each $Y(C_n)$ by the factor stated in the box.}
\label{fig:yi}
\end{figure}

@@

\begin{figure}
\plotone{cn}
\caption{
Shape of $Y(C_n)$ vs. n for $\cthree$\ to $\ceight$
at two different temperatures
near 2000K. These shapes can be understood by the relative magnitudes of
flows into and out of $\cenn$.
}
\label{fig:cn}
\end{figure}

@@

\begin{figure}
\plotone{no_gamma}
\caption{
Abundances for network containing only C, O, CO, $\ctwo$, and $\cthree$
when photodissociation of molecules is omitted. Rapid rise of $Y(CO)$
to $10^{-2}$ near 5500 K and the ratio $Y(CO)/Y(\ctwo)$ near $10^4$ are
similar to Fig. 11 of \citet{2009ApJ...703..642C}.
}
\label{fig:no_gamma}
\end{figure}

@@

\begin{thebibliography}{14}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Cherchneff} \& {Dwek}(2009)}]{2009ApJ...703..642C}
{Cherchneff}, I. \& {Dwek}, E. 2009, \apj, 703, 642

\bibitem[{{Cherchneff} \& {Dwek}(2010)}]{2010ApJ...713....1C}
---. 2010, \apj, 713, 1

\bibitem[{{Clayton}(2011)}]{2011NewAR..55..155C}
{Clayton}, D.~D. 2011, \nar, 55, 155

\bibitem[{{Clayton}(2013)}]{2013ApJ...762....5C}
---. 2013, \apj, 762, 5

\bibitem[{{Clayton} {et~al.}(2001){Clayton}, {Deneault}, \&
  {Meyer}}]{2001ApJ...562..480C}
{Clayton}, D.~D., {Deneault}, E.~A.-N., \& {Meyer}, B.~S. 2001, \apj, 562, 480

\bibitem[{{Clayton} {et~al.}(1999){Clayton}, {Liu}, \&
  {Dalgarno}}]{1999Sci...283.1290C}
{Clayton}, D.~D., {Liu}, W., \& {Dalgarno}, A. 1999, Science, 283, 1290

\bibitem[{{Clayton} \& {The}(1991)}]{1991ApJ...375..221C}
{Clayton}, D.~D. \& {The}, L.-S. 1991, \apj, 375, 221

\bibitem[{{Deneault} {et~al.}(2003){Deneault}, {Clayton}, \&
  {Heger}}]{2003ApJ...594..312D}
{Deneault}, E.~A.-N., {Clayton}, D.~D., \& {Heger}, A. 2003, \apj, 594, 312

\bibitem[{{Deneault} {et~al.}(2006){Deneault}, {Clayton}, \&
  {Meyer}}]{2006ApJ...638..234D}
{Deneault}, E.~A.-N., {Clayton}, D.~D., \& {Meyer}, B.~S. 2006, \apj, 638, 234

\bibitem[{{Klots}(1968)}]{1968...Klots}
{Klots}, C.~E. 1968, in Fundamental Processes in Radiation Chemistry, ed.
  P.~{Ausloos} (New York: Interscience)

\bibitem[{{Lepp} {et~al.}(1990){Lepp}, {Dalgarno}, \&
  {McCray}}]{1990ApJ...358..262L}
{Lepp}, S., {Dalgarno}, A., \& {McCray}, R. 1990, \apj, 358, 262

\bibitem[{{Liu} \& {Dalgarno}(1996)}]{1996ApJ...471..480L}
{Liu}, W. \& {Dalgarno}, A. 1996, \apj, 471, 480

\bibitem[{{Liu} \& {Victor}(1994)}]{1994ApJ...435..909L}
{Liu}, W. \& {Victor}, G.~A. 1994, \apj, 435, 909

\bibitem[{{Meyer} \& {Adams}(2007)}]{2007M&PSA..42.5215M}
{Meyer}, B.~S. \& {Adams}, D.~C. 2007, 70th Annual Meteoritical Society
  Meeting, held in August 13-17, 2007, Tucson, Arizona.~Meteoritics and
  Planetary Science Supplement, Vol.~42, p.5215, 42, 5215

\end{thebibliography}
